\documentclass[draft=false
              ,paper=a4
              ,twoside=false
              ,fontsize=11pt
              ,headsepline
              ,BCOR10mm
              ,DIV11
              ,bibtotoc% Bibliographie ins TOC 
              ,liststotoc% Tab./Abb.verzeichnis ins TOC
              ]{scrbook}
\usepackage[ngerman,english]{babel}
%% see http://www.tex.ac.uk/cgi-bin/texfaq2html?label=uselmfonts

%\usepackage[utf8]{inputenc}
%\usepackage[ansinew]{inputenc}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{libertine}
\usepackage{pifont}
\usepackage{microtype}
\usepackage{textcomp}
\usepackage[german,refpage]{nomencl}
\usepackage{setspace}
\usepackage{makeidx}
\usepackage{listings}
\usepackage{natbib}
\usepackage[ngerman,colorlinks=true]{hyperref}
\usepackage{soul}
\usepackage{hawstyle}
\usepackage{lipsum} %% for sample text
\usepackage[section]{placeins}
\usepackage{amsmath}

%% define some colors
\colorlet{BackgroundColor}{gray!20}
\colorlet{KeywordColor}{blue}
\colorlet{CommentColor}{black!60}
%% for tables
\colorlet{HeadColor}{gray!60}
\colorlet{Color1}{blue!10}
\colorlet{Color2}{white}

%% configure colors
\HAWifprinter{
  \colorlet{BackgroundColor}{gray!20}
  \colorlet{KeywordColor}{black}
  \colorlet{CommentColor}{gray}
  % for tables
  \colorlet{HeadColor}{gray!60}
  \colorlet{Color1}{gray!40}
  \colorlet{Color2}{white}
}{}
\lstset{%
  numbers=left,
  numberstyle=\tiny,
  stepnumber=1,
  numbersep=5pt,
  basicstyle=\ttfamily\small,
  keywordstyle=\color{KeywordColor}\bfseries,
  identifierstyle=\color{black},
  commentstyle=\color{CommentColor},
  backgroundcolor=\color{BackgroundColor},
  captionpos=b,
  fontadjust=true
}
\lstset{escapeinside={(*@}{@*)}, % used to enter latex code inside listings
        morekeywords={uint32_t, int32_t}
}
\ifpdfoutput{
  \hypersetup{bookmarksopen=false,bookmarksnumbered,linktocpage}
}{}

%% more fancy C++
\DeclareRobustCommand{\cxx}{C\raisebox{0.25ex}{{\scriptsize +\kern-0.25ex +}}}

%% TODOS markieren
\newcommand{\TODO}[1]{\colorbox{yellow}{\textcolor{red}{[TODO: #1]}}}

\clubpenalty=10000
\widowpenalty=10000
\displaywidowpenalty=10000

% unknown hyphenations
\hyphenation{
}

%% recalculate text area
\typearea[current]{last}

\makeindex
\makenomenclature

\begin{document}
\selectlanguage{ngerman}
\parindent0mm
\parskip2ex

%%%%%
%% customize (see readme.pdf for supported values)
\HAWThesisProperties{Author={Benjamin Burchard}
                    ,Title={Automatisierte Testdatenerstellung mit Klassifikationsbäumen für Web-Testing}
                    ,EnglishTitle={Automated Testdata-Generation with classification trees for Web-Testing}
                    ,ThesisType={Bachelorarbeit}
                    ,ExaminationType={Bachelorprüfung}
                    ,DegreeProgramme={Bachelor of Science Technische Informatik}
                    ,ThesisExperts={Prof. Dr. Zhen Ru Dai \and Prof. Dr. --------}
                    ,ReleaseDate={30. April 2013}
                  }

%% title
\frontmatter

%% output title page
\maketitle

\onehalfspacing

%% add abstract pages
%% note: this is one command on multiple lines
\HAWAbstractPage
%% German abstract
{Web-Testing, Klassifikationsbäume, Test-Automatisierung, Java, JUnit, Selenium, CTE }%
{Diese Arbeit hat zum Ziel mit Hilfe von Klassifikiationsbäumen und den daraus entstehenden Teställen automatisch Testdaten für Web-Testing zu erstellen. Um dies zu erreichen wird ein Java-Programm entwickelt welches aus den Daten eines Klassifikationsbaum-Tools (Classification Tree Editor XL) Testdaten für vorgefertigte Testfälle erstellt. Diese werden, unter Verwendung des Selenium Webdriver und JUnit, automatisch ausgeführt und die daraus resultierenden Ergebnisse dargestellt und ausgewertet.\\\\}
%% English abstract
{Web-Testing, classification trees, test automation, Java, JUnit, Selenium, CTE}%
{This thesis has the goal to automatically create test data for web-testing from testcases deigned by calssification trees. To achieve this, a Java program is developed which creates test data from a classification tree tool (Classification Tree Editor XL) for pre-built testcases. These will be automatically executed using Selenium Webdriver and JUnit and the resulting findings will be graphically displayed and evalued}

\newpage
\singlespacing

\tableofcontents
\newpage


%% main
\mainmatter
\onehalfspacing
%% write to the log/stdout
\typeout{===== File: chapter 1}
%% include chapter file (chapter1.tex)
%%\include{chapter1}

%%%%
%% add some text to generate a sample document
\include{./Kapitel/Chapter1_Einleitung}

\include{./Kapitel/Chapter2_Grundlagen}

\include{./Kapitel/Chapter3_Anforderungsanalyse}

%\chapter{Design}
%\section{User Interface}
%\section{Zusammenspiel}
%\section{Programmaufbau}

\include{./Kapitel/Chapter4_Implementierung}

\include{./Kapitel/Chapter5_Fallstudie}

\include{./Kapitel/Chapter6_FazitUndAusblick}
%%%%

%% appendix if used
%%\appendix
%%\typeout{===== File: appendix}
%%\include{appendix}

%% enable if these lists should be shown on their own page
\listoffigures
\listoftables
%%\lstlistoflistings

% bibliography and other stuff
\backmatter

\typeout{===== Section: literature}
%% read the documentation for customizing the style
\bibliographystyle{alpha}

\bibliography{mainBA}

\typeout{===== Section: nomenclature}
%% uncomment if a TOC entry is needed
%%\addcontentsline{toc}{chapter}{Glossar}
\renewcommand{\nomname}{Glossar}
\clearpage
\markboth{\nomname}{\nomname} %% see nomencl doc, page 9, section 4.1
\printnomenclature

%% index
\typeout{===== Section: index}
\printindex

\HAWasurency

\end{document}
